Multi-reference pangenome graphs

### 2022-01-05 manuscript/fig_induction.tex
lighter lines

\begin{pgfonlayer}{bg}    % select the background layer
\draw[line width=1,color=red!100,looseness=1] (seqA1.south) to (g1);
\draw[line width=1,color=red!100,looseness=1] (seqB1.south) to (g1);
\draw[line width=1,color=red!100,looseness=1] (seqC1.south) to (g1);

\draw[line width=1,color={rgb:red,1;orange,1},looseness=0.5] (seqA2.south) to (g2);
\draw[line width=1,color={rgb:red,1;orange,1},looseness=0.5] (seqC2.south) to (g2);

\draw[line width=1,color=orange!100,looseness=0.5] (seqA3.south) to (g4);
\draw[line width=1,color=orange!100,looseness=0.5] (seqB3.south) to (g4);
\draw[line width=1,color=orange!100,looseness=0.5] (seqC3.south) to (g4);

\draw[line width=1,color=green!100,looseness=0.5] (seqA4.south) to (g5);
\draw[line width=1,color=green!100,looseness=0.5] (seqB4.south) to (g5);
%\draw[line width=1,color=blue!100,looseness=0.5] (seqC3.south) to (g4);

\draw[line width=1,color={rgb:blue,1;green,1},looseness=0.5] (seqA5.south) to (g6);
\draw[line width=1,color={rgb:blue,1;green,1},looseness=0.5] (seqB5.south) to (g6);

\draw[line width=1,color=blue!100,looseness=0.5] (seqA6.south) to (g7);
\draw[line width=1,color=blue!100,looseness=0.5] (seqB6.south) to (g7);

\draw[line width=1,color={rgb:blue,1;purple,1},looseness=0.5] (seqA7.south) to (g8);
\draw[line width=1,color={rgb:blue,1;purple,1},looseness=0.5] (seqC5.south) to (g8);

\draw[line width=1,color=purple!100,looseness=0.5] (seqB7.south) to (g9);

\draw[line width=1,color=gray,looseness=0.5] (seqB2.south) to (g3);

>>>>

\begin{pgfonlayer}{bg}    % select the background layer
\draw[line width=0.5,color=red!100,looseness=1] (seqA1.south) to (g1);
\draw[line width=0.5,color=red!100,looseness=1] (seqB1.south) to (g1);
\draw[line width=0.5,color=red!100,looseness=1] (seqC1.south) to (g1);

\draw[line width=0.5,color={rgb:red,1;orange,1},looseness=0.5] (seqA2.south) to (g2);
\draw[line width=0.5,color={rgb:red,1;orange,1},looseness=0.5] (seqC2.south) to (g2);

\draw[line width=0.5,color=orange!100,looseness=0.5] (seqA3.south) to (g4);
\draw[line width=0.5,color=orange!100,looseness=0.5] (seqB3.south) to (g4);
\draw[line width=0.5,color=orange!100,looseness=0.5] (seqC3.south) to (g4);

\draw[line width=0.5,color=green!100,looseness=0.5] (seqA4.south) to (g5);
\draw[line width=0.5,color=green!100,looseness=0.5] (seqB4.south) to (g5);
%\draw[line width=0.5,color=blue!100,looseness=0.5] (seqC3.south) to (g4);

\draw[line width=0.5,color={rgb:blue,1;green,1},looseness=0.5] (seqA5.south) to (g6);
\draw[line width=0.5,color={rgb:blue,1;green,1},looseness=0.5] (seqB5.south) to (g6);

\draw[line width=0.5,color=blue!100,looseness=0.5] (seqA6.south) to (g7);
\draw[line width=0.5,color=blue!100,looseness=0.5] (seqB6.south) to (g7);

\draw[line width=0.5,color={rgb:blue,1;purple,1},looseness=0.5] (seqA7.south) to (g8);
\draw[line width=0.5,color={rgb:blue,1;purple,1},looseness=0.5] (seqC5.south) to (g8);

\draw[line width=0.5,color=purple!100,looseness=0.5] (seqB7.south) to (g9);

\draw[line width=0.5,color=gray,looseness=0.5] (seqB2.south) to (g3);
